Computer Science House Constitution

### 2022-02-15 constitution.tex
Add references to range of qualifications

\documentclass{article}
\providecommand{\RevisionInfo}{}
\usepackage{hyperref}
% Reformat section titles
\usepackage{titlesec}

@@

\asubsection{Waiving of Qualifications}
\begin{enumerate}
  \item The following Qualifications may be waived as decided by a Two-Thirds Immediate Vote as described in \ref{Two-Thirds} and \ref{Immediate Vote}:
    \begin{enumerate}
      \item Candidates must reside on floor during the term of office.
      \item Candidates must have at least one full semester of House membership as an Active Member.
      \item Social and Research and Development are the only voting Executive Board positions that allow for Dual Directorship.
    \end{enumerate}
  \item Each vote to waive a Qualification must only apply to a single Qualification and a single Selection.
  \item The chair of the vote shall state what qualification waiver is being voted upon, what Selection the waiver will apply to, and any nominated candidates not qualified under \ref{Qualifications} who would become qualified if the waiver passes.
\end{enumerate}

>>>>

\documentclass{article}
\providecommand{\RevisionInfo}{}
\usepackage{hyperref}
% Reformat section titles
\usepackage{titlesec}
\usepackage{cleveref}

@@

\asubsection{Guidelines on Overriding Executive Board Qualifications}
\begin{itemize}
\item This section provides no definitions, instead serving to clarify the applicability of Overrides to Qualifications in the Selection of members of the Executive Board.
\item When executing a Constitutional Override \ref{Semantic Changes} for a Qualification specified in sections {\crefname{Qualifications}{}{}\crefrange{Qualifications to be the Chairperson, Evaluations Director}{Qualifications to be the House Secretary or an Ad Hoc Director}}, the Override shall apply to a specific qualification of the directorship, and if passed, to all candidates for said directorship.
\end{itemize}
